%-------------------------------------------------------------------------------
%	TITLE
%-------------------------------------------------------------------------------
\cvsection{EXPERIENCE}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


  \cventry
    {Senior Full-stack Engineer}
    {WeTransfer}
    {WeTransfer was founded in 2009 as the simplest way to send big files around the world. Now it's a whole suite of productivity tools that take care of other tricky bits of the creative process.}
    {Amsterdam, Netherlands (Remote)}
    {07/2022 - Present}
    {
      \begin{cvitems}
        \item{Reduce resource costs by analysing usage on AWS S3 and freeing terrabytes of orphaned objects.}
        \item{Planned and implemented optimisation of a MySQL database with more than 100k of transactions per second.}
        \item{Designed and implemented a framework to write go services with ease.}
        \item{Developed a system to get encrypted backend errors and traces directly from end-users.}
        \item{Interacted with different stakeholders and internal customers throughout the company.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Development Engineer} % Job title
    {ELEVEN SPORTS HQ} % Organization
    {ELEVEN is serving millions of customers with live and on demand content and enabling hundreds of partners to live stream their matches every month.}
    {Amsterdam, Netherlands (Remote)} % Location
    {11/2020 - 07/2022} % Date(s)
    {
      \begin{cvitems}
        \item{Developed and maintained 40+ services, jobs, and internal tools using Go, gRPC and GraphQL.}
        \item{Reduced complexity and technical costs via designing asynchronous serverless message passing architecture using kafka, websockets and durable objects on CloudFlare workers platform.}
        \item{Improved resiliency of the system against DDoS attacks by utilising envoy proxy rate limit service and integrating it with the backend services.}
        \item{Designed and implemented viewer concurrency control system as a CloudFlare worker.}
        \item{Designed and implemented user subscriptions with recurring payments supporting multiple payment service providers.}
        \item{Migrated legacy search and explore service from NodeJS to Go.}
        \item{Implemented remote telemetry gateway service to support external analytics integrations.}
        \item{Designed and implemented asset management service and standardised bucket naming by implementing a common library.}
        \item{Implemented match exploration APIs for a FIFA project.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full-stack Developer} % Job title
    {L'île des Médias / ViaDirect} % Organization
    {ViaDirect is an interactive solution that guides and informs visitors of public places.}
    {Paris, France (Remote)} % Location
    {03/2019 - 11/2020} % Date(s)
    {
      \begin{cvitems}
        \item{Responsible for integration of their products with Google Calendar.}
        \item{Standardized APIs using RFC3339 to support different time zones across the globe.}
        \item{Optimized code on VDLights embedded boards.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-Founder and Director of Technology} % Job title
    {Quiz of Kings} % Organization
    {Quiz of Kings is a social trivia mobile game. It has 18M+ registered users and 2.5M+ monthly active users.}
    {Tehran, Iran} % Location
    {04/2015 - 10/2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Planned company OKRs along with the CEO and other C-level members.}
        \item {Built strategic relationship with datacenters and other tech companies to provide affordable and profitable services.}
        \item {Leaded designing architecture to build several grpc microservices via \emph{Gin, Vitess, Redis and etcd.}}
        \item {Initiated and coordinated the deployment a large scale sharded \emph{MySQL} database (over 200 nodes) using \emph{Vitess}.}
        \item {Coordinated the implementation of a cheat detection system which uses many factors to find potential cheaters and ban them.}
        \item {Coordinated building a fully automated CI/CD pipelines via \emph{Gitlab CI} for testing and deploying containerized applications to Kubernetes.}
        \item {Implemented \emph{Agile} methodology across departments to guarantee success in a highly dynamic ecosystem.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Architect} % Job title
    {Snappfood} % Organization
    {Snappfood is the leading online food ordering company in Iran.}
    {Tehran, Iran} % Location
    {06/2014 - 04/2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented \emph{RESTful API} server for web and mobile application via \emph{Symphony2, MySQL, and Redis}.}
        \item {Migrated all of data from Microsoft SQL Server into Galera Cluster for MySQL.}
        \item {Redesigned and migrated legacy code in ASP.Net to PHP.}
        \item {Implemented \emph{geographic/geometric algorithms} to define restaurant delivery zones, delivery fees, etc.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Mobile Application Developer} % Job title
    {Turned On Digital} % Organization
    {TOD is a full service mobile services agency based in the UK and the ME.}
    {Tehran, Iran} % Location
    {10/2013 - 06/2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on a multi-platform Javascript mobile application made with Titanium SDK.}
      \end{cvitems}
    }


\end{cventries}

